### 2025-03-15 paper/sections/other/main_results.qmd
table fixed and I need a break after this latex nightmare

tbl_mtbl = final_mutability(mtbl_dir; var=["distance"])
df = final_table(res_dir; tbl_mtbl)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
tabulate_results(inputs; table_type=:tabular, save_name="paper/quarto_ecml/tables/main.tex", wrap_table=false)
tabulate_results(inputs; table_type=:tabular, save_name="paper/preprint/tables/main.tex", wrap_table=false)
```

>>>>

tbl_mtbl = final_mutability(mtbl_dir; var=["distance"])
df = final_table(res_dir; tbl_mtbl)
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
formatters = (
    PrettyTables.ft_round(1,findall(.!contains.(names(df),"Acc"))),
    PrettyTables.ft_round(2,findall(contains.(names(df),"Acc")))
)
for fname in ["paper/quarto_ecml/tables/main.tex","paper/preprint/tables/main.tex"]
    tabulate_results(
        inputs; 
        table_type=:tabular, 
        save_name=fname, 
        wrap_table=false, 
        alignment=[:c,fill(:r,size(df,2)-1)...],
        formatters=formatters
    )
end
```
